### 2015-03-02 fundamentals/intro.tex
clarifying archetype definition, as suggested by @flanflanagan

This structure recognizes that specialists should utilize their time and
resources in modeling the specific process associated with their area of
expertise (e.g., reprocessing and advanced fuel fabrication), without having to
create a model of the entire fuel cycle to serve as its host.  \Cyclus supports
them by separating the problem of modeling a physics-dependent supply chain into
two distinct components: a simulation kernel and archetypes that interact with
the kernel. The kernel is responsible for supporting the deployment and
interaction logic of entities in the simulation.  Physics calculations and
customized behaviors are implemented within archetypes.

>>>>

This structure recognizes that specialists should utilize their time and
resources in modeling the specific process associated with their area of
expertise (e.g., reprocessing and advanced fuel fabrication), without having to
create a model of the entire fuel cycle to serve as its host.  \Cyclus supports
them by separating the problem of modeling a physics-dependent supply chain into
two distinct components: a simulation kernel and archetypes that interact with
it. The kernel is responsible for supporting the deployment and
interaction logic of entities in the simulation.  Physics calculations and
customized behaviors of those entities are implemented within \emph{archetype}
classes.
